---
title: "GGPLOT2 PROJECT"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

---
title: "Recreating the Corruption and Human Data Plot"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(data.table)
```

### Load data


```{r load-data}
df <- fread('Economist_Assignment_Data.csv',drop=1)
```



* * *

## Part 1: Data
```{r}
head(df)
```
 

* * *

## Part 3: Plotting


```{r}
pl <- ggplot(df,aes(x=CPI,y=HDI,color=Region)) + geom_point()
pl

```

Telling whther a movie was popular or not after it has been selected(or awarded) for an oscar award seems pointless since it would be obvious that one would like to predict the movie's popularity beforehand.


Checking for null(missing) values

```{r}

pl <- ggplot(df,aes(x=CPI,y=HDI,color=Region)) + geom_point(size=4,shape=1)
pl
```



```{r}
pl + geom_smooth(aes(group=1))
```


```{r}
pl2 <- pl + geom_smooth(aes(group=1),method ='lm',formula = y~log(x),se=FALSE,color='red')
pl2
```

```{r}
pl2 + geom_text(aes(label=Country))
```


```{r}
pointsToLabel <- c("Russia", "Venezuela", "Iraq", "Myanmar", "Sudan",
                   "Afghanistan", "Congo", "Greece", "Argentina", "Brazil",
                   "India", "Italy", "China", "South Africa", "Spane",
                   "Botswana", "Cape Verde", "Bhutan", "Rwanda", "France",
                   "United States", "Germany", "Britain", "Barbados", "Norway", "Japan",
                   "New Zealand", "Singapore")

pl3 <- pl2 + geom_text(aes(label = Country), color = "gray20", 
                data = subset(df, Country %in% pointsToLabel),check_overlap = TRUE)

pl3
```


```{r}

pl4 <- pl3 + theme_bw() 
pl4
```


```{r}

pl5 <- pl4 + scale_x_continuous(name = "Corruption Perceptions Index, 2011 (10=least corrupt)",
                     limits = c(.9, 10.5),breaks=1:10) 
pl5
```





```{r}

pl6 <- pl5 + scale_y_continuous(name = "Human Development Index, 2011 (1=Best)",
                     limits = c(0.2, 1.0))
pl6
```


```{r}

pl6 + ggtitle("Corruption and Human development")
```


```{r}
library(ggthemes)
pl6 + theme_economist_white()
```









